Implications of afforestation policies for global markets

### 2024-02-26 paper.Rmd
Update paper.Rmd

Table 1
	                         ∆ (%)
Central America	                -16.9
East Asia	                -14.4
North Africa & the Middle East	-11.1
Southeast Asia	                -10.0
Russia	                         -9.8
Brazil	                         -9.7
Rest of South America	        -14.7
South Asia	                 -9.1
Canada	                         -8.1
Oceania	                         -7.5
European Union	                 -6.4
Sub-Saharan Africa	         -4.8
EUII	                         -3.3
China	                         -2.5
United States	                 -2.1
Japan	                         11.4

@@

Table 2
			∆ (%)
East Asia		-5.9
Southeast Asia		-2.8
Central America		-2.7
South Asia		-2.1
Rest of South America	-1.6
North Africa & the Middle East	-1.2
Sub-Saharan Africa	-0.5
China			-0.1
Russia			0.1
Brazil			0.2
EUII			0.3
European Union		0.4
United States		0.8
Oceania			0.9
Canada			1.3
Japan			1.5

@@

Table 3
				∆ (%)
				Agriculture
Japan				13.5
United States			5.0
Canada				2.6
Russia				2.4
Oceania				2.2
EUII				2.2
China				1.5
European Union			1.4
Brazil				1.4
Sub-Saharan Africa		0.0
North Africa & the Middle East	-2.3
Rest of South America		-3.8
Central America			-6.9
Southeast Asia			-7.3
South Asia			-11.0
East Asia			-19.8

@@

Table 4
				∆ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
EUII				-588,500,000
Brazil				-735,125,000
United States			-1,085,000,000
Russia				-1,152,375,000
Rest of South America		-3,848,625,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
European Union			-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

>>>>

Table 1 qo-Land
	                         ∆ (%)
Central America	                -16.9
East Asia	                -14.4
North Africa & the Middle East	-11.1
Southeast Asia	                -10.0
Russia	                         -9.8
Brazil	                         -9.7
Rest of South America	        -14.7
South Asia	                 -9.1
Canada	                         -8.1
Oceania	                         -7.5
European Union	                 -6.4
Sub-Saharan Africa	         -4.8
EUII	                         -3.3
China	                         -2.5
United States	                 -2.1
Japan	                         11.4

@@

Table 2 qo-Ag
			∆ (%)
East Asia		-5.9
Southeast Asia		-2.8
Central America		-2.7
South Asia		-2.1
Rest of South America	-1.6
North Africa & the Middle East	-1.2
Sub-Saharan Africa	-0.5
China			-0.1
Russia			0.1
Brazil			0.2
EUII			0.3
European Union		0.4
United States		0.8
Oceania			0.9
Canada			1.3
Japan			1.5

@@

Table 3 qxw-Ag
				∆ (%)
				Agriculture
Japan				13.5
United States			5.0
Canada				2.6
Russia				2.4
Oceania				2.2
EUII				2.2
China				1.5
European Union			1.4
Brazil				1.4
Sub-Saharan Africa		0.0
North Africa & the Middle East	-2.3
Rest of South America		-3.8
Central America			-6.9
Southeast Asia			-7.3
South Asia			-11.0
East Asia			-19.8

@@

Table 4 EV
				∆ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
EUII				-588,500,000
Brazil				-735,125,000
United States			-1,085,000,000
Russia				-1,152,375,000
Rest of South America		-3,848,625,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
European Union			-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

Much of this loss in well-being may be the result of higher prices. Japan is the only nation that sees any positive price impacts resulting from this policy, with the price of agricultural goods decreasing 0.2 percent (table 5). All other regions, for both agricultural and non-agricultural products, see prices rise between 0.1 and 2.8 percent.

Table 5 pm
									∆ (%)				
	Agricultural Goods		Forest Products		Lumber		Paper Products		Other Non-Agricultural Goods
Oceania					0.6	0.3	0.3	0.3	0.3
China					0.7	0.3	0.2	0.2	0.3
Japan					-0.2	0.2	0.2	0.2	0.2
East Asia				2.8	0.2	0.2	0.2	0.2
Southeast Asia				1.5	0.2	0.2	0.2	0.2
South Asia				1.6	0.2	0.2	0.1	0.2
Canada					0.4	0.3	0.3	0.3	0.4
United States				0.4	0.3	0.3	0.3	0.3
Central America				1.3	0.2	0.2	0.2	0.2
Brazil					0.7	0.3	0.3	0.3	0.3
Rest of South America			1.1	0.2	0.2	0.2	0.2
European Union				0.5	0.2	0.2	0.2	0.2
EUII					0.6	0.3	0.2	0.2	0.2
Russia					0.6	0.2	0.2	0.2	0.2
Sub-Saharan Africa			0.9	0.3	0.2	0.2	0.3
North Africa & the Middle East		1.1	0.2	0.2	0.2	0.2

Land price seems weird. I have it decreasing????
